---
title: "Untitled"
author: "tu"
date: "8/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggimage)
library(geofacet)
theme_set(theme_minimal())

tuesdata <- tidytuesdayR::tt_load(2020, week = 32)

type <- tuesdata$energy_types %>% filter(level == "Level 1")
total <- tuesdata$country_totals
```
```{r fig.height=10, fig.width=16}
#two_data <- 
total %>% 
  pivot_longer(
    cols = starts_with("20"),
    names_to = "year_usage",
    values_to = "energy_usage"
  ) %>% 
  replace_na(list(country_name = "United Kingdom")) %>% 
  group_by(country, country_name, type) %>% 
  summarise(energy_usage = sum(energy_usage)) %>% 
  full_join(prep) %>% 
  ungroup() %>% 
  filter(type %in%  c("Energy supplied","Exports")) %>% 
  pivot_wider(
    names_from = type,
    values_from = energy_usage
  ) %>% 
  mutate(
    unfulfilled = -(New_tech-`Energy supplied`)/`Energy supplied`
  ) %>% 
  ggplot(aes(reorder(country_name, unfulfilled),unfulfilled))+
  geom_col()+
  coord_flip()
  # geom_text(aes(label = country))
```
```{r}
total %>% 
  pivot_longer(
    cols = starts_with("20"),
    names_to = "year_usage",
    values_to = "energy_usage"
  ) %>% 
  replace_na(list(country_name = "United Kingdom")) %>% 
  group_by(country, country_name, type) %>% 
  summarise(energy_usage = sum(energy_usage)) %>% 
  full_join(prep) %>% 
  ungroup() %>% 
  filter(country == "NO")
  
```


```{r}
#emis_data <- 
annual_co2_emissions_per_country %>% 
  filter(Year %in% c(2016, 2017, 2018)) %>% 
  group_by(Entity) %>% 
  summarise(emission = sum(`Annual CO₂ emissions (tonnes)`)) %>% 
  right_join(two_data , by = c("Entity" = "country_name")) %>% 
  left_join(co_emissions_per_capita %>% 
              filter(Year %in% c(2016, 2017, 2018)) %>% 
              pivot_wider(
                    names_from = Year,
                    values_from = `Per capita CO₂ emissions (tonnes)`
              )
            ) %>% 
  ggplot()+
  geom_col(aes(
    
  ))
  
```

```{r}
emis_data %>% 
  ggplot(
    aes(
      decarb_pct,
      `2018`,
      color = color
    )
  ) +
  geom_point() 
  # geom_text(
  #   aes(
  #     label = Entity
  #   )
  # )
```

# how decarb_pct and imports pct correlated?
more decarb more import
```{r fig.height=10, fig.width=10}
emis_data %>% 
  #filter(color == "cov") %>% 
  pivot_wider(
    names_from = type,
    values_from = energy_usage
  ) %>% 
  # mutate(
  #   ex = Exports/(`Total net production` + Exports)
  # ) %>% 
  ggplot(
    aes(
      decarb_pct*100,
      `2018`,
      color = color
    )
  ) +
  geom_point(
    
  ) +
  geom_text(
    aes(
      label = Entity
    )
  )
  # ylim(0,0.5) +
  # xlim(0, 1)
```

# 主要想探知对新旧能源得生产是否和能量的去处/用途有什么关系
increasing the share of low-carbon energy sources, particularly renewables, and a corresponding reduction in the use of fossil fuels

CO2
 emissions in the power sector were unchanged in 2017, and rose economy-wide. Low hydro and
nuclear generation coupled with increasing demand led to increasing fossil generation. So despite
the large rise in wind generation, we estimate power sector CO2
 emissions remained unchanged at
1019 million tonnes. However, overall stationary emissions in the EU emissions trading sectors rose
slightly from 1750 to 1755 million tonnes because of stronger industrial production especially in rising
steel production. Together with additional increases in non-ETS gas and oil demand, we estimate
overall EU greenhouse gas emissions rose by around 1% in 2017. 

## 是不是越decarbonised 就越独立，Imports越少

```{r}
flag_data <- data.frame(
  image = c("PT", "ES"),
  x = c(110, 110),
  y = c(19.1, 50.1)
)

## ggplot2 code ##
ggplot()+
geom_flag(data = flag_data,
          aes(x = x, y = y,
              image = image), size= 0.2
          )  
## ggplot2 code ##
```

