---
title: "Untitled"
author: "Tu"
date: "6/22/2020"
output: html_document
---

```{r}
library(tidyverse)
library(bbplot)
library(lubridate)
theme_set(theme_minimal())
```

```{r}
beer_states <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-31/beer_states.csv') %>%
  na.omit()
```
```{r}
write.csv(beer_states,".\\beer_states.csv", row.names = FALSE)
```

```{r}
skimr::skim(beer_states)
```

```{r}
head(beer_states)
```

## What is the most common/produced type throughout the years?
```{r}
beer_states %>%
  count(type)
```
 
```{r}
beer_states %>%
  group_by(type) %>%
  tally(barrels)
```
 
 ## Where is this difference from? Which state produces the most of bottles of cans?
 ## Which year is the boost?
 
```{r fig.height=22, fig.width=11}
beer_states %>%
  filter(!str_detect(state, "total")) %>%
  group_by(state,type) %>%
  tally(barrels) %>%
  arrange(desc(n)) %>%
  ggplot() +
  geom_col(aes(x = n, y = reorder(state,n), fill = type))
```
 
 

```{r fig.height=22, fig.width=11}
beer_states %>%
  filter(state == "ND") %>%
    group_by(type) %>%
    tally(barrels) 
```

## I wonder what happen to those low production states?(SD,ND,WV) geographical reasons? climate? but people in Dokoda likes heavy drinking:
No causal relationship between drinking habits and Beer production

## Is there any sober group? geographical reason? economy reason? that I can draw


## what is the distribution of CO throughout years? 
```{r}

```


## Styling code
```{r include = FALSE}
styler::tidyverse_style()
```

 