---
title: "EDA"
author: "Tu"
date: "6/11/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
windowsFonts(Helvetica = "TT Arial")
```

```{r include=FALSE}
library(tidyverse)
library(bbplot)
theme_set(theme_minimal())
```


```{r warning=FALSE, include=FALSE}
vb_matches <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-19/vb_matches.csv', guess_max = 76000) 
  # %>%
  # filter(w_p1_country == w_p2_country | l_p1_country == l_p2_country)
```


## Knwon: serve is a disadvantage because it provides chances for opponent to attack.

```{r}
#vb_matches %>%
 # skimr::skim() 
```



```{r fig.height=20, fig.width=20}
vb_tot <- vb_matches %>%
  transmute(
    across(circuit:gender),
    w_attacks = w_p1_tot_attacks + w_p2_tot_attacks,
    w_kills = w_p1_tot_kills + w_p2_tot_kills,
    w_errors = w_p1_tot_errors + w_p2_tot_errors,
    w_aces = w_p1_tot_aces + w_p2_tot_aces,
    w_serveerrors = w_p1_tot_serve_errors + w_p2_tot_serve_errors,
    w_blocks = w_p1_tot_blocks + w_p2_tot_blocks,
    w_digs = w_p1_tot_digs + w_p2_tot_digs,
    l_attacks = l_p1_tot_attacks + l_p2_tot_attacks,
    l_kills = l_p1_tot_kills + l_p2_tot_kills,
    l_errors = l_p1_tot_errors + l_p2_tot_errors,
    l_aces = l_p1_tot_aces + l_p2_tot_aces,
    l_serveerrors = l_p1_tot_serve_errors + l_p2_tot_serve_errors,
    l_blocks = l_p1_tot_blocks + l_p2_tot_blocks,
    l_digs = l_p1_tot_digs + l_p2_tot_digs
  )%>%
  pivot_longer(w_attacks:l_digs,
               names_to = 'stat',
               values_to = 'value') %>%
  separate(col = "stat",
           into = c("win_lose", "technique"),
           sep = "_",
           extra = "merge") 

```




# Hypothesis 1: Winning team should be good at attacking to score
# Hypothesis 2: Winning team should be good at blocking and digging

## I am going to look at winning teams' behavior, compare to losing teams. 

```{r}
vb_tot %>%
  na.omit() %>%
  # replace_na(list(value = 0)) %>%
  ggplot(aes(gender, value, color = win_lose, fill = win_lose)) +
  geom_violin(alpha = 0.4) +
  facet_wrap(~technique, scales = "free_y") 
  
```

Observation 1: Without na.omit() there a ton of missing values.

# i wanna make a table. Variable name: Percentage of missing values.

```{r}
vb_tot %>%
  group_by(technique) %>%
  summarise(pct = mean(is.na(value)),
            n = n()) 
```
Now I am heading to player-level data. See if the score really match with the used techiques per match




```{r}
vb_tot %>%
  #filter(win_lose == "w") %>%
  replace_na(list(value = 0)) %>%
  group_by(technique, win_lose) %>%
  summarise(most_tech = sum(value)) %>%
  arrange(desc(most_tech)) %>%
  ggplot(aes(technique, most_tech, fill = as.factor(win_lose))) +
  geom_bar(stat = "identity", position="dodge") +
  geom_hline(yintercept = 0, size = 1, colour="#333333") +
  bbc_style() +
  scale_fill_manual(values = c("#1380A1", "#FAAB18"))
  
```
Less errors.
Less attacks.
More digs;
more blocks;
more kills


# I also wonder the distribution of techniques per match or tournament or country. At those various conditions(gaming country, home country, gender, age), which technique is the most popular?

I am going to dive into player level data and find out!


```{r include=FALSE}
vb_player_match <- 
  vb_matches %>%
  # separate the name. (all the names with _ symbol)
  rename(w_p1_name = w_player1, w_p2_name = w_player2,
         l_p1_name = l_player1, l_p2_name = l_player2,
         w_team_rank = w_rank, l_team_rank = l_rank) %>%
  mutate_at(vars(starts_with('w_'), starts_with('l_')), as.character) %>%
  pivot_longer(
    cols = c(starts_with("w_"),starts_with("l_"))) %>%
  separate(col = "name",
           into = c("win_lose", "player","stats"),
           sep = "_",
           extra = "merge") %>%
  rename(tournament_country = country) %>%
 
  # dont wanna name and birthdate and age stacked
  # this might be dangerous...I might sum the dig, kill...of two players
  pivot_wider(names_from = 'stats', 
             values_from = 'value',
             names_repair = 'unique') %>%
  type_convert() %>%
  filter(player != "team") %>%
  
  #split score
  separate_rows(score, sep = ",") %>%
  mutate(score = str_remove(score, ' retired')) %>%
  mutate(score = na_if(score, "Forfeit or other")) %>%
  separate(score, c('w_score', 'l_score'), sep = "-")
  

```

```{r fig.height=15, fig.width=20}
vb_player_match %>%
  replace_na(list(tot_digs = 0)) %>%
 # filter(tot_attacks != 0) %>%
 # pivot_longer(tot_attacks:tot_digs,
  #             names_to = 'stat',
   #            values_to = 'value') %>%
  ggplot() +
  geom_density(aes(x = tot_digs, colour = win_lose, fill = win_lose), alpha=0.2) +
  facet_wrap(~ country, scales = "free", nrow = 10)

```

### It is unreasonable to claim that NAs in total techniques are 0 because a lot of countries(Algeria, Iceland and Nigeria etc..) their data are just not recorded.
```{r}
vb_player_match %>%
  filter(country == 'Algeria') %>%
  View()
# algeria technique data is all NA???!!!
```
```{r}
vb_matches %>%
  filter(l_p2_country == "Algeria") %>%
  View()
  
```


```{r}
vb_player_match %>%
  replace_na(list(tot_digs = 0)) %>%
  filter(tot_attacks != 0) %>%
 # pivot_longer(tot_attacks:tot_digs,
  #             names_to = 'stat',
   #            values_to = 'value') %>%
  ggplot() +
  geom_density(aes(x = tot_digs, colour = win_lose, fill = win_lose), alpha=0.2) +
  facet_wrap(~ circuit, scales = "free", nrow = 10)
```



## observations before filter(!=0), 
so many missing values in each country
some countries dont use attacks???? -> it's just not recorded

## things i wanna find out:
* players from which country have the highest winning rate
```{r}
head(vb_player_match)

```

```{r}
vb_player_match %>%
  group_by(country) %>%
  summarise(win_pct = mean(win_lose == "w")) %>%
  arrange(desc(win_pct))
```

Do brazilian players also show up both in AVP and FIVB?
```{r}
#both_t_country <- 
  vb_player_match %>%
  group_by(country, circuit) %>%
  summarise(win_pct = mean(win_lose == "w")) %>%
  ungroup() %>%
  pivot_wider(names_from = "circuit",
              values_from = "win_pct") %>%
  na.omit() %>%
 # filter(FIVB != 0 & AVP != 0) %>%
  arrange(desc(FIVB))
```
```{r fig.height=30}
both_t_country %>%
  mutate(country = fct_reorder(country, FIVB)) %>%
  pivot_longer(cols = FIVB:AVP,
               names_to = "game",
               values_to = "winning_rate") %>%
  ggplot() +
  geom_bar(aes(winning_rate, country, fill = game),
           stat = 'identity',
           position = 'dodge') +
  scale_fill_brewer()
               
```
```{r }
library(hrbrthemes)
update_geom_font_defaults()

p <- both_t_country %>%
  mutate(diff = round(FIVB - AVP,2),
         country = fct_reorder(country, diff))
```
```{r fig.height=18}

plot <- ggplot(data = p, aes(x = country, y = diff, label=diff)) +
  geom_segment(aes(x = country, xend = country,
                   y = 0, yend = diff), 
               color = "black") +
  geom_point(stat='identity', fill="black", size=18) +
  coord_flip() +
  geom_text(color="white", size=6) +
 # bbc_style() +
  theme(
      panel.grid.minor.y = element_blank(),
      panel.grid.major.y = element_blank(),
      legend.position="none"
    )
plot
```


Ok, they do.
Then, 
* in which country do Brazilian players lose the most? 
```{r}
vb_player_match %>%
  mutate_at(vars(match_num), as.character) %>%
  filter(country == "Brazil" ) %>%
  group_by(tournament_country) %>%
  summarise(
    win_pct = mean(win_lose == "w")
    )
  
```

* why is there a difference in those two circuits?
* because they serve more in AVP?
* rules not favored?
* which year?
* do men play worse?
```{r}
vb_player_match %>%
 # mutate_at(vars(match_num), as.character) %>%
  filter(country == "Brazil" ) %>%
  group_by(tournament_country) %>%
  distinct(match_num) %>%
  arrange(desc(match_num))
  
```
So countries with 0 winning percent actually do not win
```{r}
vb_player_match %>%
  filter(country == "Fiji" & circuit == "FIVB")
```


## Height? does FIVB and AVP winning rate have anything to do with player's height from each country?
* replace height na with average height of each country
```{r}
height <- vb_player_match %>%
  group_by(country) %>%
  summarise(avg_height = mean(hgt, na.rm = TRUE)) %>%
  ungroup() 
  
win_pct <- vb_player_match %>%
  group_by(country, circuit) %>%
  summarise(win_pct = mean(win_lose == "w"),
           ) %>%
  ungroup() %>%
  pivot_wider(names_from = "circuit",
              values_from = "win_pct") %>%
  na.omit()

data <- left_join(win_pct, height)
```



```{r fig.height=10, fig.width=15}
data %>%
    pivot_longer(cols = FIVB:AVP,
               names_to = "game",
               values_to = "winning_rate") %>%
  
  ggplot(aes(avg_height, winning_rate, colour = game)) +
  geom_point() +
  geom_line() +
  geom_text(aes(label = country), check_overlap = TRUE)
```

What is going on with 
```{r}
vb_player_match %>% 
  filter(country == "Russia" | country == "Moldova") %>% 
  count(country)
```

em...Russia is a very experienced country...number of matching games should account for difference of average winning percent

* add a column to data that includes number of total games for each country
```{r}
vb_matches %>%
  count(bracket)
```

## If USA matches with another USA team, one wins and the other one loses. Then the winning rate of USA becomes 50%. Therefore, winning rate is not a good abstract of information
