---
title: "EDA"
author: "Tu"
date: "2020/5/24"
output: github_document
---

```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

theme_set(theme_minimal())
```

```{r include=FALSE}
vb_matches <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-19/vb_matches.csv', guess_max = 76000)
```



```{r}
#skimr::skim(vb_matches)
```
```{r}
head(vb_matches)
```

```{r}
vb_parsed <- vb_matches %>%
  transmute(
    circuit,
    gender,
    year,
    w_attacks = w_p1_tot_attacks + w_p2_tot_attacks,
    w_kills = w_p1_tot_kills + w_p2_tot_kills,
    w_errors = w_p1_tot_errors + w_p2_tot_errors,
    w_aces = w_p1_tot_aces + w_p2_tot_aces,
    w_serve_errors = w_p1_tot_serve_errors + w_p2_tot_serve_errors,
    w_blocks = w_p1_tot_blocks + w_p2_tot_blocks,
    w_digs = w_p1_tot_digs + w_p2_tot_digs,
    l_attacks = l_p1_tot_attacks + l_p2_tot_attacks,
    l_kills = l_p1_tot_kills + l_p2_tot_kills,
    l_errors = l_p1_tot_errors + l_p2_tot_errors,
    l_aces = l_p1_tot_aces + l_p2_tot_aces,
    l_serve_errors = l_p1_tot_serve_errors + l_p2_tot_serve_errors,
    l_blocks = l_p1_tot_blocks + l_p2_tot_blocks,
    l_digs = l_p1_tot_digs + l_p2_tot_digs
  ) %>%
  na.omit()
```

```{r}
winners <- vb_parsed %>%
  select(circuit, gender, year,
         w_attacks:w_digs) %>%
  rename_with(~ str_remove_all(., "w_"), w_attacks:w_digs) %>%
# . means piping in all columns
  mutate(win = 'win')

losers <- vb_parsed %>%
  select(circuit, gender, year,
         l_attacks:l_digs) %>%
  rename_with(~ str_remove_all(., "l_"), l_attacks:l_digs) %>%
  mutate(win = "lose")

vb_df <- bind_rows(winners, losers) %>%
  mutate_if(is.character, factor) # change anything that is character to factor
```


```{r}
vb_df %>%
  pivot_longer(attacks:digs, names_to = 'stat', values_to = 'value') %>%
  # pivot_longer would make things easier to plot
  ggplot(aes(gender, value, fill = win, color = win))+
  geom_violin(alpha = 0.2)+
  # a = 0.4, othersie you cant see the median from the graph
  facet_wrap(~stat, scales = 'free_y', nrow = 2) +
     # free_y because the value vary
  labs(y = NULL, color = NULL, fill = NULL)
  # y = null becasue of 
 
```

```{r}
vb_df %>%
  pivot_longer(attacks:digs, names_to = "stat", values_to = "value") %>%
  ggplot(aes(gender, value, fill = win, color = win)) +
  geom_boxplot(alpha = 0.4) +
  facet_wrap(~stat, scales = "free_y", nrow = 2) +
  labs(y = NULL, color = NULL, fill = NULL)
```

Generally, it looks like digs, blocks, aces and less errors result in victory.

## Keep exploring
```{r}
head(vb_matches)
```
### To lookup number of matches on various conditions(date, city)

```{r}
vb_matches %>%
  count(circuit, tournament, date, sort = TRUE)
```


### use pivot_longer

```{r}
vb_long <- vb_matches %>%
  rename(w_p1_name = w_player1, w_p2_name = w_player2,
         l_p1_name = l_player1, l_p2_name = l_player2,
         w_team_rank = w_rank, l_team_rank = l_rank) %>%
  mutate_at(vars(starts_with('w_'), starts_with('l_')), as.character) %>%
  pivot_longer(
    cols = c(starts_with("w_"),starts_with("l_"))
  ) %>%
  separate(col = 'name', into = c('winner_loser','player', 'name'), 
           sep = '_', 
           extra = "merge",
           #fill = "right"
           ) 
  # now we dont wanna birhtdate things to stack upon each other
  

```
```{r}
vb_players <- vb_long %>%
  rename(tournament_country = country) %>%
  filter(name != "rank") %>%
  pivot_wider(names_from = name, values_from = value, names_repair = "unique") %>%
  type_convert()
  
```

## Let's deal with the scores now

start over from vb_matches and pan it out vertically
```{r}
vb_sets <- vb_matches %>%
  mutate(match_id = row_number()) %>%
  select(match_id, circuit:match_num, score) %>%
  separate_rows(score, sep = ",") %>%
  mutate(score = str_remove(score, ' retired')) %>%
  mutate(score = na_if(score, "Forfeit or other")) %>%
  separate(score, c('w_score', 'l_score'), sep = "-")
```

```{r}
vb_sets %>%
  mutate(winner_won = w_score > l_score) %>% 
  group_by(match_id) %>%
  summarise(pct_won = mean(winner_won)) %>%
  ungroup()
```

## players

```{r}
by_players <- vb_players %>%
  group_by(name, gender) %>%
  summarize(n_matches = n(),
            pct_winner = mean(winner_loser == "w"),
            first_game = min(date),
            last_game = max(date)) %>%
  arrange(desc(n_matches)) %>%
  ungroup()
```
```{r}
by_players %>%
  filter(n_matches >= 200) %>%
  ggplot(aes(n_matches, pct_winner, color = gender))+
  geom_point() +
  scale_x_log10() +
  scale_y_continuous(labels = scales::percent)
  
```


## what fraction of data is not null
```{r}
vb_players %>%
  summarize_all(~ mean(!is.na(.))) %>%
  gather() %>%
  View()

```


## some tournament even dont have many total attacks(or other techniques)
```{r}
vb_players %>%
  group_by(tournament) %>%
  summarise(pct_win = mean(!is.na(tot_attacks)),
            n = n()) %>%
  # mean of true and false is percentage
  arrange(desc(pct_win))
  
```

## how to judge a player from 































